---
title: "**QDNAseq**"
author: "Michael Bell,  15002484" 
date: "05/01/2022"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

# **Quantitative DNA Sequencing for Chromosomal Aberrations**
# **QDNAseq R Package**

## **Introduction:**  
Chromosomal aberrations are defined as a change within either the structure or number of a chromosome. Most typical chromosomal aberrations are considered to be aneuploids; meaning they contain or are missing a number of chromosomes (e.g trisomy and monosomy) (Abhishek, K. J. a. D. S. a. K. D. a. R. M. a. A. K. P. (2018). 


When you click the **Knit** button a document will be generated that includes both content as well as the output of any embedded R code chunks within the document. You can embed an R code chunk like this:

```{r cars}
summary(cars)
```

## Including Plots
 
You can also embed plots, for example:

```{r pressure, echo=FALSE}
plot(pressure)
```

Note that the `echo = FALSE` parameter was added to the code chunk to prevent printing of the R code that generated the plot.
